PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-07-25 qfenv_paper/qf_environment.tex
Finished preliminary analysis for SMF and QF.
Also has summary outline?

\begin{abstract}
We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). Our stellar mass limited galaxy sample consists of $\sim 40000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 130000$ SDSS galaxies within $z = 0.0375-0.145$. We classify the galaxies as quiescent or star-forming, based on an evolving specific star formation cut, and as low or high density environments, based on fixed cylindrical aperture environment measurements on a volume-limited {\em Environment Definition Population} (from PRIMUS and SDSS). For each of these subsamples, we examine the stellar mass function (SMF) evolution and compute the $f_{\rm{Q}}(\mathcal{M}_{*})$. We find that in both low and high density environments the quiescent fraction increases with cosmic time over the probed redshift range. Moreover, the difference between the quiescent fraction in low and high density environments remains constant throughout the redshift range. These results suggest that the evolution of the quiescent fraction is independent of environment and provide constraints on quenching mechanisms in high density environments such as groups and clusters.  
\end{abstract}

@@

\begin{table} %Subject to significant change based on the classification of environment
  \caption{Galaxy Subsamples}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
      &$z$ &Environment        &Quiescent  &Star-forming  \\ \hline 
  SDSS      &$0.0375-0.145$ &High           &5470                       &4501                           \\
            &               &Low            &5419                       &8927                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.2-0.4$      &High           &322                    &583                           \\
            &               &Low            &768                    &2516                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.4-0.6$      &High           &350                       &675                           \\
            &               &Low            &871                       &2385                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.6-0.8$      &High           &347                       &430                           \\
            &               &Low            &833                       &1847                           \\
            &               &               &                       &                           \\ \hline
  PRIMUS    &$0.8-1.0$      &High           &136                       &232                           \\
            &               &Low            &373                       &810                           \\
            &               &               &                       &                           \\ \hline
  \multicolumn{5}{l}{}                                             \\       
    \end{tabular} 
  \end{center}
\end{table}

@@

\subsection{Galaxy Sample} \label{sec:target} 
Using the low redshift SDSS-{\em GALEX} and intermediate redshift PRIMUS data described above, in this section, we define our galaxy sample which will be used to compute the SMFs and QFs. For PRIMUS, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for their parent sample. We take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude limits on optical selection bands as specified in \cite{Moustakas:2013aa} Table 1. These limits are in different optical selection bands and have distinct values for the five PRIMUS target fields. We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$). In addition we impose a redshift range of $ 0.2 < z < 0.8$ for the PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations from sample variance and $ z < 0.8$ is selected due to the lack of sufficient statistics in subsamples defined below.

@@

In order to consistently measure environment throughout our entire sample we impose PRIMUS redshift errors on our SDSS galaxies. However, we observe a significant difference between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin. For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments. 
As a result, we note that the SMF redshift evolution is inconsistent when transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.

Yet, just from the PRIMUS samples alone, we probe a sufficient redshift range to observe certain trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}.

Examining the SMF evolution from $z \sim 0.7$ to $z \sim 0.1$, we find that in high density environments both the star-forming and quiescent SMFs increase at $\mathcal{M}_{*}$ below the knee of mass function ($\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 10.75$ for star-forming; $\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 11.0$ for quiescent). Meanwhile, at masses above the knee the SMFs for high density environments exhibit little change over the entire cosmic time range.

At low density environments, the quiescent SMF remains relatively constant for galaxies with $\rm{log}\: \mathcal{M}_{*}/\mathcal{M}_{\odot} < 10.75$. At higher stellar masses, however, the quiescent low density environment SMF decreases notably. Finally, the low density environment star-forming SMF shows a decrease at all stellar mass ranges over the redshift range. We caution readers and reserve any detailed analysis of the SMF evolution to future work due to the improvements in photometry that significantly alter the lowest redshift bin SMFs mentioned in Section \ref{sec:sdss}.

%Compare SMFs at low environment vs high environment and remark that the SMFs are significantly different. 
%Remark on the clear mass-density relation: more massive galaxies in high environment 
% Compare to Bolzonella et al. 2010 and  Bundy et al. 2006 results
% Agree with previous works on mass segregation results from VVDS, DEEP2, and etc.

@@

Many physical mechanisms have been proposed to explain the quenching of star-formation observed in our universe. Often star-formation quenching is parameterized using two distinct mechanisms: mass-dependent and environment dependent mechanisms (Baldry et al. 2006 Peng et al. 2010). By the mass-dependence in all $f_{\rm{Q}}$ in Figure \ref{fig:qf} we conclude that galaxy stellar mass plays a significant role in quenching. Furthermore, from the fact that $f_Q$ in high density environments is always greater than $f_Q$ in low density environments, our results also reflect the environment dependence in quenching. However, in many of the proposed environment dependent quenching mechanisms, the quenching time scale is proposed to decrease. This would result in an increase in the quenched fraction that's faster than the increase in low density environment $f_Q$. We find that this is not the case. % What does this have to say about physical processes in groups and clusters that affect quenching?

\section{Summary} \label{sec:summary}
Using a stellar mass complete galaxy sampled derived from SDSS and PRIMUS accompanied by a consistently measured galaxy environment from robust spectroscopic redshifts, we demonstrate that the quiescent fraction increases over cosmic time for $ z < 0.8$, regardless of environment. During this epoch the quiescent fraction in high density environments is consistently greater than the quiescent fraction in low density environments. Furthermore, when we fit the quiescent fraction at a fiducial mass ($\mathcal{M}_{\rm{fid}}$), we find that the evolution of the quiescent fraction from $z \sim 0.8$ to $z \sim 0.1$ is similar for high and low density environments.

\begin{itemize}
	\item 1. SMFs in low and high environment are different for both SF and Q
	\item 2. Mass dependence of QF
	\item 3. redshift dependence of Qf
	\item 4. environment dependence of QF
	\item 5. QF fit 
\end{itemize}

We thank ...
%
% References
%
\bibliography{PRIMUS}

>>>>

\begin{abstract}
We investigate the effects of galaxy environment on the evolution of the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using spectroscopic redshifts and multi-wavelength imaging data from PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey (SDSS). Our stellar mass limited galaxy sample consists of $\sim 40000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 130000$ SDSS galaxies within $z = 0.0375-0.145$. We classify the galaxies as quiescent or star-forming, based on an evolving specific star formation cut, and as low or high density environments, based on fixed cylindrical aperture environment measurements on a volume-limited {\em Environment Definition Population} (from PRIMUS and SDSS).

For each of these subsamples, we examine the stellar mass function (SMF) evolution and compute the $f_{\rm{Q}}(\mathcal{M}_{*})$. We find that in both low and high density environments the quiescent fraction increases with cosmic time over the probed redshift range. Moreover, the difference between the quiescent fraction in low and high density environments remains constant throughout the redshift range. These results suggest that the evolution of the quiescent fraction is independent of environment and provide constraints on quenching mechanisms in high density environments such as groups and clusters.  
\end{abstract}

@@

\begin{table} %Subject to significant change based on the classification of environment
  \caption{Galaxy Subsamples}
  \label{tab:subsample}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
    $z$ &Environment        &Quiescent  &Star-forming  \\ \hline 
$0.0375-0.145$ &High           &5470                       &4501                           \\
               &Low            &5419                       &8927                           \\
               &               &                       &                           \\ \hline
$0.2-0.4$      &High           &322                    &583                           \\
               &Low            &768                    &2516                           \\
               &               &                       &                           \\ \hline
$0.4-0.6$      &High           &350                       &675                           \\
               &Low            &871                       &2385                           \\
               &               &                       &                           \\ \hline
$0.6-0.8$      &High           &347                       &430                           \\
               &Low            &833                       &1847                           \\
               &               &                       &                           \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} 
  \end{center}
\end{table}

@@

\subsection{Galaxy Sample} \label{sec:target} 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primuszerr_masslimit_histogram.png,height=0.5\textwidth}
     \caption{Environment measure distribution for our galaxy sample.}      \label{fig:envcount}
    \end{center}
\end{figure*}

Using the low redshift SDSS-{\em GALEX} and intermediate redshift PRIMUS data described above, in this section, we define our galaxy sample which will be used to compute the SMFs and QFs. For PRIMUS, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for their parent sample. We take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and impose magnitude limits on optical selection bands as specified in \cite{Moustakas:2013aa} Table 1. These limits are in different optical selection bands and have distinct values for the five PRIMUS target fields. We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$). In addition we impose a redshift range of $ 0.2 < z < 0.8$ for the PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations from sample variance and $ z < 0.8$ is selected due to the lack of sufficient statistics in subsamples defined below.

@@

Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we observe a significant discrepancy between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin. For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments. As a result, we caution that the SMF redshift evolution is inconsistent during the transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.

Yet, from the PRIMUS samples alone, we probe a sufficient redshift to observe notable trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}. Later we compare these trends to SMF results from DEEP2 (\cite{bundy06a}) and zCOSMOS (\cite{Bolzonella:2010aa}). In panel (a), star-forming galaxies in low density environments, we find a significant decrease in the high mass end of the SMF ($\mathcal{M} > 10^{10.75} \mathcal{M}_{\odot}$). In contrast at lower masses ($\mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) we observe a notable increase in the SMF. In panel (b), star-forming galaxies in high density environments, we notice a possible decrease above the knee of the SMF ($\mathcal{M} \sim 10^{10.7} \mathcal{M}_{\odot}$) accompanied by an increase below the knee. For the quiescent population in low density environment, shown in panel (c) of Figure \ref{fig:smf}, we notice an increase in $\Phi$ for lower masses, but we do not notice any clear SMF evolution at the massive end. Lastly for the quiescent population in high density environments, panel (d), we find significant increase in $\Phi$ at all masses.

In comparison to \cite{bundy06a} and \cite{Bolzonella:2010aa}, some of the noted trends are not immediately evident. However, this is mostly due to the conflicting mass limits proposed in each study. Not to mention, only part of the redshift range probed by \cite{bundy06a} overlap with our results. Overall, we find that the trends we note in the SMF evolution above are in good agreement with results from DEEP2 and zCOSMOS.

Observing the evolutionary trends in SMF for each of these sub-populations simultaneously provides a naive narrative of the different galaxy evolutionary tracks involving environment and quenching. For example, the decrease in the massive star-forming galaxies in low density environment over cosmic time can be attributed to the transition of those galaxies to any of the other panels. The star-forming galaxies in low density environments that have quenched their star formation over time are possibly responsible for the increase of the quiescent, low density environment SMF over time. The star-forming galaxies that fall into higher density environments explain the increase in the star-forming high density environment SMF below the knee. Finally, star-forming galaxies in high density environments that have quenched their star-formation, quiescent galaxies that have transitioned from low to high density environments, and star-forming galaxies in low density environments that quench their star-formation while infalling to high density environments all contribute to the overall increase of the high environment quiescent SMF.

In addition to the evolution over cosmic time, we observe noticeable trends when we compare the SMFs for star-forming and quiescent galaxies between the two environments. Comparison of the SMFs in low versus high density environments reveal a noticeable relation between mass and density, with SMFs in high density environments having more massive galaxies. We further confirm this trend when we compare the median mass between the two environments to find that the median mass for galaxies in high density environments is significantly greater than in low density environments. The relationship between mass and environment observed in our SMFs mirror the well-established mass-density relation and observed mass segregation with environment in the literature (\cite{bundy06a}; \cite{Scodeggio:2009aa}; \cite{Bolzonella:2010aa}).

We caution readers and reserve detailed analysis of the SMFs to future work due to the improvements in photometry that significantly alter the SDSS SMFs mentioned in Section \ref{sec:sdss}. 
% There is also the issue with the SMF evolution: the uneven fractional contribution of the population and each environment classification.

@@

Many physical mechanisms have been proposed to explain the quenching of star-formation observed in our universe. Often star-formation quenching is classified into two distinct mechanisms: mass-dependent and environment dependent mechanisms (\cite{Baldry:2006aa}; \cite{Peng:2010aa}). From the mass-dependence presented in all $f_{\rm{Q}}$ in Figure \ref{fig:qf}, we concur that galaxy stellar mass plays a significant role in quenching. Furthermore, since $f_Q$ in high density environments is always greater than $f_Q$ in low density environments, our results also reflect the environment dependence in quenching. %However, in many of the proposed environment dependent quenching mechanisms, the quenching time scale is proposed to decrease. This would result in an increase in the quenched fraction that's faster than the increase in low density environment $f_Q$. We find that this is not the case. % What does this have to say about physical processes in groups and clusters that affect quenching?

\section{Summary} \label{sec:summary}
Using a stellar mass complete galaxy sampled derived from SDSS and PRIMUS accompanied by a consistently measured galaxy environment from robust spectroscopic redshifts, we measure the stellar mass functions for star-forming and quiescent in low and high density environments over the redshift range $z < 0.8$. From these stellar mass functions, we compare the proportion of quiescent galaxies within the subsamples by computing quiescent fraction for each of them. Afterwards, in order to better quantify the evolution of the quiescent fraction over cosmic time, we fit our quiescent fraction anchored at a fiducial mass. From our analyses we find the following notable results.

\begin{enumerate}
	\item By noting the SMF evolution for each of our subsamples, we loosely trace the evolutionary tracks our galaxy population tracing the general evolutionary tracks of quenching mechanisms and galaxies infalling into high density environments. 
	\item From the SMFs, we find that our galaxy population in high density environments, both star-forming and quiescent, have a higher median mass, thus confirming the mass density relation and mass-segregation in different environments.
	\item In all of our subsamples, we find a clear mass dependence in $f_{\rm{Q}}$. $f_{\rm{Q}}$ increases monotonically with galaxy stellar mass. 
	\item Both from the $f_{\rm{Q}}$ evolution and $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ values, $f_{\rm{Q}}$ increases with redshift. 
	\item We conclude, by fitting our $f_{\rm{Q}}$, that $f_{\rm{Q}}$ in high density environments is greater than $f_{\rm{Q}}$ in low density environments regardless of mass and redshift. This result confirms the environmental dependence of quenching mechanisms stated previously in literature. 
	\item Comparison of the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ evolution for high and low density environments that the total evolution is independent of environment. 
\end{enumerate}

%  demonstrate that the quiescent fraction increases over cosmic time for $ z < 0.8$, regardless of environment. During this epoch the quiescent fraction in high density environments is consistently greater than the quiescent fraction in low density environments. Furthermore, when we fit the quiescent fraction at a fiducial mass ($\mathcal{M}_{\rm{fid}}$), we find that the evolution of the quiescent fraction from $z \sim 0.8$ to $z \sim 0.1$ is similar for high and low density environments.

We thank people...
%
% References
%
\bibliography{PRIMUS}
